The paper on \Large \bf Blockchain Frontrunning

### 2018-09-13 frontrunning/Latex/sections/paper.tex
[frontrunning] ICO frontrunning

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Recently, researchers have shown that Bancor is vulnerable to front running attacks. Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users. There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants \cite{NewTab13:online}.
%______________________________________________________________%
\subsection{Name Services.}

@@

%icos are easy to be missed in the overall most used apps. 
%Make subsections here. one for ico's and why they are important and not in the most used daaps ones. one for  status ico, and different ones for each part
%justify why ICOs were missed in the previous section. argue why 100 other things like ICOs that were missing from the list . ICOs were missed becasue no ico was happening there, and also the website filteres through known applications, we could not think of any other scenarios that are similar to icos.

As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.

@@

According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.

>>>>

Bancor is another Ethereum-based application that allows users to exchange their tokens without any counter-party risk. This protocol aims to solve the cryptocurrency liquidity issue by introducing \textit{Smart Tokens}~\cite{hertzog2017bancor}-- ERC20 compatible tokens with a built-in liquidity mechanism that are always available to users. Smart Tokens can be bought and sold through the users smart contract at an automatically calculated price which displays supply and demand. Doing so, Bancor protocol provides continuous liquidity for digital assets without relying on an order book as there is no requirement to match sellers and buyers.
Recently, researchers have shown that Bancor is vulnerable to front running attacks. Implemented on the Ethereum blockchain, when Bancor transactions are broadcast to the network, they sit in a pending transaction pool known as \textit{mempool} waiting for the miners to mine them. Since Bancor handles all the trades and exchanges on the Ethereum blockchain (unlike other existing decentralized exchanges), these transactions are all visible to the public for 16s (the average Ethereum blocktime) before being included within a block. This leaves this blockchain-based decentralized exchange vulnerable to the blockchain race condition attack as attackers are given enough time to front-run other transactions and gain favorable profits~\cite{BancorIs7:online}. As mentioned in Section~\ref{sec:who can front-run?} and same as every other Ethereum based application, Bancor transactions can be front run by miners and other regular (non-miner) users. There is an implementation of a Bancor front running attack in the Python programming language which represent how a non-miner user can front run other network participants~\cite{NewTab13:online}.
%______________________________________________________________%
\subsection{Name Services.}

@@

There has been more than 3000 ICOs on Ethereum alone, estimated to exceed 75 billion dollars in the first half of 2018~\cite{zetzsche2018ico}. On our DApp samples there was not ICOs mainly because they tend to run for a short time with high number of participant and in the time of writing no ICOs have reached the top 25 DApps of \texttt{DAppradar.com}. Needless to say the importance of ICOs as an application of blockchain requires more in-depth analysis of front-running on these DApps. %ICOs due to the defined cap, are similar to our analogy of a queue line, people would line up to get in and there's a opportunity to front-run. 
Here we focus on one ICO that our preliminary research showed that there might be a front-running attack going on. There is no doubt that similar behaviour could be seen on other instances of ICOs or similar DApps if investigated.

\subsection{\textit{Status.im} ICO}
As discussed in~\ref{sec:Front Running on the Blockchains}, capped ICOs are considerable applications to be investigated in terms of the front-running attacks, \textit{Status.im} ICO is such application. In June 2017, \textit{Status.im}~\cite{statuswhitepaper} started its ICO and reached the defined cap within 3 hours, resulting in close to 300,000 Ether of funds. In order to prevent few large investments to buy up all the tokens and limit the amount of Ether deposited in an investment, they used a \textit{fair} token distribution method named \textit{Dynamic Ceiling} as an attempt to increase the time window for smaller investors. They implemented multiple caps --ceiling-- in which, each had a maximum amount that could be deposited in. In this case, every deposit was checked by the smart contract and the exceeding amount was refunded to the sender while the accepted amount was sent to their multisignature wallet address ~\cite{statusicoanalysis}.

@@

\subsection{Data Collection and Analysis}
According to the analysis we carried out, it was discovered that the F2Pool, an Ethereum mining pool that had around 23\% of the mining hash rate at the time (Figure ~\ref{fig:mining_pool_ratio}), sent 100 Ether to 30 new Ethereum addresses before Status.im ICO started. On the time the ICO was opened for participation, F2Pool constructed 31 transactions to the ICO token sale smart contract from the addresses they controlled --without broadcasting these transactions to the network-- and used their entire mining power to mine their own transactions and also potentially failing high gas price transactions.
